
\documentclass[letterpaper,11pt]{resume-chinese}
\usepackage[UTF8]{ctex}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{5pt}\scshape\raggedright\Large
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]


	%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \vspace{+2pt}
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

	\newcommand{\resumeSubheading}[4]{
  \vspace{+5pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


	\newcommand{\resumeSubItemTime}[2]{
  \vspace{5 pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-18pt}
}

\newcommand{\resumeSubItem}[2]{\vspace{+4pt}\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://muhualing.github.io/}{\Huge Mu Hualing}} & Email :
  \href{mailto:hualing.mu@outlook.com}{hualing.mu@outlook.com}\\
  \href{http://github.com/muhualing}{http://github.com/muhualing} & \href{tel: +86 18069867372}{Mobile: +86 18069867372} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Zhejiang University}{Hangzhou, China}
      {Master of Computer Technology;  GPA: 3.85}{Sep. 2017 -- Apr. 2020}
     
    \resumeSubheading
      {Hefei University of Technology}{Anhui, China}
      {Bachelor of Applied Mathematics;  GPA: 3.53}{Sep. 2013 -- Jun. 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

          
    \resumeSubheading
      {Microsoft}{}
      {Software Engineer Intern}{May. 2019 - Aug. 2019}
      \resumeItemListStart
        \resumeItem{Calendar Insight Bot}
          {Designed and worked across the full stack to build a bot integrated with Microsoft Teams. This bot can help users check and manage their schedules in the chat windows.}
          
      \resumeItemListEnd
    
    \resumeSubheading
      {Chuang Lin Tech}{}
      {Machine Learning Intern}{Jan. 2019 - Feb. 2019}
      \resumeItemListStart
        \resumeItem{Social media algorithm}
          {Developed and improved an PageRank algorithm which works for Weibo on big data to calculate the influence of Key Opinion Leader(KOL), lead to 10x speed boost.}
        \resumeItem{Heterogeneous database migration}
        {Use Apache Sqoop to transfer 1000GB of data in MySQL safely and efficiently (60-70MB/S) to distributed database HIVE.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Surgical robot image guidance system}
        {Designed and developed databases and controllers using MongoDB and Python for surgical imaging guidance systems for surgical planning and surgical navigation.}
    \resumeSubItem{Video real-time transmission system}
        {A set of software and hardware combined video transmission system, based on H.264 encoding acquisition encoder data, video management system based on Spring and Hibernate, using Netty to manage socket.}
    \resumeSubItem{Weshare SPA}
        {Designed and worked across the backend of Weshare by using Flask and MySQL. Weshare is a prototype of a mobile app based on Flask and React, which is a single-page app for users to post and share idle items to people around.}
    \resumeSubItem{Information Extraction for Open Domain}
        {Using BiLSTM+CRF to do word-based Chinese sequence labeling model. Import DGCNN+Residual structure, improved the speed by 3x and F1-score by 7\% on Baidu SKE dataset.}
  \resumeSubHeadingListEnd


%--------Technical SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Java, Python, SQL, Javascript, Shell, Web}
    \resumeSubItem{Specialties}
      {Back-end engineering, Front-end engineering, AWS, Natural Language Processing, Data Processing}
 \resumeSubHeadingListEnd

%--------Awards and Honors------------
\section{Awards and Honors}
 \resumeSubHeadingListStart
    \resumeSubItemTime
    {2nd Prize of National Post-Graduate Mathematical Contest in Modeling}
    {Oct. 2019}
    \resumeSubItemTime
    {1st Prize of "Bloom Cup" 5G Application Collection Competition(Led by MIIT)}
    {July. 2019}
    \resumeSubItemTime
    {Outstanding Graduate Student at Zhejiang University}
    {June. 2018, June. 2019}
    \resumeSubItemTime
    {CUMCM 2nd Prize of Anhui Province}
    {June. 2016}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
